Full Title of Article\titlebreak This Title Has A Line Break

### 2021-09-03 Submission/Paper/ML4H/Paper.tex
added tables 3 + 4

%% Table 1 - Demographics of Dataset %%
\begin{table*}[hbtp]
\floatconts
{tab:table1}
\centering 
{\caption{Demographics of Data}} \\
    {
        \begin{tabular}{lccc}
        \toprule
        \bfseries Characteristic & \bfseries (N = 16428) \\
        \midrule
        \textbf{Age (years) mean (SD)} & \fseries 73.01 (7.96) \\ 
        \textbf{Gender Male, \emph n (\%)}  & \fseries 8740 (53.2)\\ 
        \textbf{Race, \emph n (\%)} \\ 
            \hspace{10mm} White & 14896 (90.7) \\
            \hspace{10mm} Other/Not Recorded & 608 (3.7) \\
            \hspace{10mm} Black & 570 (3.5) \\
            \hspace{10mm} Hispanic & 170 (1.0) \\
            \hspace{10mm} Asian & 168 (1.0) \\
            \hspace{10mm} Indigenous & 16 (0.01) \\
        \textbf{APOE Genotype, \emph n (\%)} \\ 
            \hspace{10mm} {APOE ${\bm{\varepsilon}}$2 & 2028 (12.3)} \\
            \hspace{10mm} {APOE ${\bm{\varepsilon}}$3 & 10177 (62.0)} \\
            \hspace{10mm} {APOE ${\bm{\varepsilon}}$4 & 4223 (25.7)} \\
        \textbf{Average Speciality Visits (SD)} & 1.67 (4.6) \\ 
        \textbf{Average PCP Encounters (SD)} &  5.25 (5.63) \\ 
        % \textbf{Encounters AVG (SD)} & 14.55 (23.2) \\
        % \textbf{Keyword Matches AVG (SD)} & 26 (54.03) \\
        \bottomrule
        \end{tabular}

    }
\end{table*}

@@

We evaluated each model using a prediction threshold to maximize the accuracy and calculated performance metrics based on that threshold. Model performance for each model in shown in Table 2. All performance metrics are based on the sequence level class assignments. % discuss sequence level stats (notes above)%

@@

% Table 2 - Results
\begin{table}[hbtp]
\floatconts
{tab:table2}
  {\begin{tabular}{lcccccccc}
    \toprule 
    \bfseries Model & \bfseries AUC & \bfseries Accuracy & \bfseries Sensitivity & \bfseries Specificity & \bfseries Micro F1  & \bfseries Macro F1 & \bfseries Weighted F1 \\ 
    \midrule
    TF-IDF & 0.95 & 0.84 & 0.83 & 0.92 & 0.84 & 0.814 & 0.843 \\
    \bottomrule
  \end{tabular}}
  {\caption{Model Performance}}
\end{table}

\section{Conclusion and Future Work} 
\label{sec:ConclusionFutureWork} We applied innovative Machine Learning and Deep Learning NLP techniques to identify patients with cognitive impairment in EHR. Our work can help combat the issues of underdiagnosis and misdiagnosis for dementia. % {More coming soon } %

@@

% Appendix B
\section{Keywords} % wi
\begin{table}[hbtp] 
\floatconts
{tab:keywords}
    {\caption{Keywords indicative of Cognitive Impairment}} \\
    {
        \begin{tabular}{lccc}
        \toprule
        \bfseries Keyword & \bfseries Match Count\\
        \midrule

@@

        \bottomrule
        \end{tabular}
    }
\end{table}

>>>>

%% Table 1 - Demographics of Dataset %%
\begin{table*}[hbtp]
\floatconts
{tab:table1}
\centering 
    {
        \begin{tabular}{lccc}
        \toprule
        \bfseries Characteristic & \bfseries (N = 16428) \\
        \midrule
        \textbf{Age (years) mean (SD)} & \fseries 73.01 (7.96) \\ 
        \textbf{Gender Male, \emph n (\%)}  & \fseries 8740 (53.2)\\ 
        \textbf{Race, \emph n (\%)} \\ 
            \hspace{10mm} White & 14896 (90.7) \\
            \hspace{10mm} Other/Not Recorded & 608 (3.7) \\
            \hspace{10mm} Black & 570 (3.5) \\
            \hspace{10mm} Hispanic & 170 (1.0) \\
            \hspace{10mm} Asian & 168 (1.0) \\
            \hspace{10mm} Indigenous & 16 (0.01) \\
        \textbf{APOE Genotype, \emph n (\%)} \\ 
            \hspace{10mm} {APOE ${\bm{\varepsilon}}$2 & 2028 (12.3)} \\
            \hspace{10mm} {APOE ${\bm{\varepsilon}}$3 & 10177 (62.0)} \\
            \hspace{10mm} {APOE ${\bm{\varepsilon}}$4 & 4223 (25.7)} \\
        \textbf{Average Speciality Visits (SD)} & 1.67 (4.6) \\ 
        \textbf{Average PCP Encounters (SD)} &  5.25 (5.63) \\ 
        % \textbf{Encounters AVG (SD)} & 14.55 (23.2) \\
        % \textbf{Keyword Matches AVG (SD)} & 26 (54.03) \\
        \bottomrule
        \end{tabular}
        {\caption{Demographics of Data}} \\
    }
\end{table*}

@@

We evaluated each model using a prediction threshold to maximize the accuracy and calculated performance metrics based on that threshold. Model performance for each model in shown in \tableref{tab:table2}. All performance metrics are based on the sequence level class assignments. % discuss sequence level stats (notes above)%

@@

% Table 2 - Results
\begin{table*}[hbtp]
\floatconts
{tab:table2}
  {\begin{tabular}{lcccccccc}
    \toprule 
    \bfseries Model & \bfseries AUC & \bfseries Accuracy & \bfseries Sensitivity & \bfseries Specificity & \bfseries Micro F1  & \bfseries Macro F1 & \bfseries Weighted F1 \\ 
    \midrule
    TF-IDF & 0.95 & 0.84 & 0.83 & 0.92 & 0.84 & 0.814 & 0.843 \\
    \bottomrule
  \end{tabular}}
  {\caption{Model Performance}}
\end{table*}

% Table 3 + 4 - Relation of Med/ICD Codes to Model Predictions
\begin{table*}[hbtp]
\floatconts
{tab:table3}
\centering 
  {\begin{tabular}{cccccc}
    \toprule 
    \bfseries  & \bfseries Count & \bfseries Yes (\%) & \bfseries No/Ntr (\%)  & \bfseries Med/ICD Code (\%)  \\ 
    \midrule
    \bfseries{APOE ${\bm{\varepsilon}}$2} & \fseries 1754 & \fseries 0.15 & \fseries 0.85 & \fseries 0.11  \\
    \bfseries{APOE ${\bm{\varepsilon}}$3} & \fseries 8751 & \fseries 0.15 & \fseries 0.85 & \fseries 0.11  \\
    \bfseries{APOE ${\bm{\varepsilon}}$4} & \fseries 3436 & \fseries 0.18 & \fseries 0.82 & \fseries 0.17  \\

    \bottomrule
  \end{tabular}}
{\caption{Comparison between Other Indicators of Cognitive Impairment and TF-IDF}} \\
\end{table*}

\begin{table*}[hbtp]
\floatconts
{tab:table4}
\centering 
    {\begin{tabular}{cccccc}
    \toprule 
    \bfseries  & \bfseries Count & \bfseries Yes (\%) & \bfseries No/Ntr (\%)  & \bfseries Med/ICD Code (\%) \\ 
    \midrule
    \bfseries{APOE ${\bm{\varepsilon}}$2} & \fseries 1754 & \fseries 0.15 & \fseries 0.85 & \fseries 0.11  \\
    \bfseries{APOE ${\bm{\varepsilon}}$3} & \fseries 8751 & \fseries 0.15 & \fseries 0.85 & \fseries 0.11  \\
    \bfseries{APOE ${\bm{\varepsilon}}$4} & \fseries 3436 & \fseries 0.18 & \fseries 0.82 & \fseries 0.17  \\

    \bottomrule
  \end{tabular}}
  {\caption{Comparison between Other Indicators of Cognitive Impairment and Clinical-BERT}} \\
\end{table*}

%% Conclusion + Future Work %%
\section{Conclusion and Future Work} 
\label{sec:ConclusionFutureWork} We applied innovative Machine Learning and Deep Learning NLP techniques to identify patients with cognitive impairment in EHR. Our work can help combat the issues of underdiagnosis and misdiagnosis for dementia. % {More coming soon } %

@@

% Appendix B
\section{Keywords} % wi
\begin{table}[hbtp] 
\floatconts
{tab:keywords}
    {\begin{tabular}{lccc}
        \toprule
        \bfseries Keyword & \bfseries Match Count\\
        \midrule

@@

        \bottomrule
        \end{tabular}}
        {\caption{Keywords indicative of Cognitive Impairment}} \\

\end{table}
